\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-10-23 metatheory-condensed.tex
Add beta rule for recursion
Add beta rule.
metatheory sec intro text

@@

  \quad \goodTerm{\Gamma, \pi^j_2\tau[(id, a)]}{b}{El~("W"~T)}}
{\goodTerm{\Gamma}{"Wsup"~T~a~b}{El~("W"~T)} }

@@

  Orthogonally, can you add the beta rule?

@@

  In other words, this recursor linkage "rec" can be used for any inductive type with signature $\tau$.\\
  Yes I will add beta rule. I see the last comment.

@@

>>>>

We contribute \TT, a core type theory that incorporates the core elements
of family polymorphism into
\citeauthor{martin1982constructive} dependent type theory~\cite{martin1982constructive},
while maintaining consistency and canonicity.

Most notably, \TT extends MLTT with what we call \emph{linkages}
(a namesake of the construct through which \citet{zm2017} model family
polymorphism in an OO setting).
Linkages model families, so they are like tuples, but with a twist: they
support late binding.

\TT is intended as a foundational model. So unlike our user-facing plugin,
typing is structural rather than nominal, and
it supports family polymorphism by providing MLTT-style judgments that
can be used to encode core aspects of the language supported by our
plugin, rather than building them in directly.
%
For example, \TT supports the extension of inductive types through
judgments that enable the further binding of W-types~\cite{martin1984intuitionistic} in linkages.
Also unlike our plugin, \TT does not feature automations such as
the generation of propositional equalities and partial recursors,
but it is expressive enough to encode their definitions.

\newpage

@@

  \quad \goodTerm{\Gamma, \pi^j_2\tau[(id, a)]}{b}{El~("W"~T)[\pi_1]}}
{\goodTerm{\Gamma}{"Wsup"~j~T~a~b}{El~("W"~T)} }

@@

@@

  In other words, this recursor linkage "rec" can be used for any inductive type with signature $\tau$.

@@

\Rule[name=Rec-Beta]
{\goodTerm{\Gamma}{h}{\cL("RecSig"~\tau~R)} 
\\ \goodTerm{\Gamma}{T}{\bW\tau}}
{\goodTerm{\Gamma}{"Wrec"~h~("Wsup"~j~T~a~b) \equiv 
("app"~(("app"~("prjR"~j~h))[("id", a)]))[("id", "lam" ("Wrec"~h[\pi_1]~b))]
}{R}}\EDJ{"app" and "lam" are lambda application and abstraction}
